%! Author = codeclabs-cn
%! Date = 2022/12/30

\section{Pointer and Reference Expressions}\label{sec:pointer-and-reference-expressions}
No spaces around period or arrow. Pointer operators do not have trailing spaces.

The following are examples of correctly-formatted pointer and reference expressions:
\begin{minted}{C++}
x = *p;
p = &x;
x = r.y;
x = r->y;
\end{minted}
Note that:
\begin{itemize}
    \item There are no spaces around the period or arrow when accessing a member.
    \item Pointer operators have no space after the \mintinline[breakanywhere,bgcolor=code_bg_pro]{C++}{*} or \mintinline[breakanywhere,bgcolor=code_bg_pro]{C++}{&}.
\end{itemize}
When referring to a pointer or reference (variable declarations or definitions, arguments, return types, template parameters, etc), you may place the space before or after the asterisk/ampersand. In the trailing-space style, the space is elided in some cases (template parameters, etc).
\begin{minted}{C++}
// These are fine, space preceding.
char *c;
const std::string &str;
int *GetPointer();
std::vector<char *>

// These are fine, space following (or elided).
char* c;
const std::string& str;
int* GetPointer();
std::vector<char*>  // Note no space between '*' and '>'
\end{minted}

You should do this consistently within a single file. When modifying an existing file, use the style in that file.

It is allowed (if unusual) to declare multiple variables in the same declaration, but it is disallowed if any of those have pointer or reference decorations. Such declarations are easily misread.
\begin{minted}{C++}
// Fine if helpful for readability.
int x, y;
\end{minted}

\begin{minted}[mathescape,
    bgcolor=code_bg_con,
    linenos,
    numbersep=5pt,
    autogobble, % 左对齐
    breaklines,
    frame=lines,
    framesep=2mm]{C++}
int x, *y;  // Disallowed - no & or * in multiple declaration
int* x, *y;  // Disallowed - no & or * in multiple declaration; inconsistent spacing
char * c;  // Bad - spaces on both sides of *
const std::string & str;  // Bad - spaces on both sides of &
\end{minted}
